% !TEX program = xelatex

\documentclass{resume}
% \usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

% \usepackage{contour}
% \usepackage{ulem}
% \normalem
% \renewcommand{\ULdepth}{1.8pt}
% \contourlength{0.8pt}

% \newcommand{\myuline}[1]{%
%   \uline{\phantom{#1}}%
%   \llap{\contour{white}{#1}}%
% }

\name{Fanchen Bu}

\basicInfo{
  \email{boqvezen97@kaist.ac.kr} \textperiodcentered\ 
  \phone{(+82) 10-4359-1551} \textperiodcentered\   
  }
\basicInfo{
\linkedin[LinkedIn: vezen-bu]{https://www.linkedin.com/in/vezen-bu}  
\github[GitHub: bokveizen]{https://github.com/bokveizen}  
  \homepage[Personal homepage]{https://bokveizen.github.io}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Korea Advanced Institute of Science and Technology (KAIST)}, South Korea}{2022.03 -- Present}
\textit{Ph.D. student} in Electrical Engineering\\
{\small Supervisor: Prof. Kijung Shin}
\datedsubsection{\textbf{Korea Advanced Institute of Science and Technology (KAIST)}, South Korea}{2019.09 -- 2021.08}
\textit{M.S.} in Electrical Engineering\\
{\small Thesis: A Novel Optimization Algorithm with Orthogonality for Deep Neural Networks Inspired by Feedback Integrators}\\
{\small Supervisor: Prof. Dong Eui Chang}
\datedsubsection{\textbf{University of Chinese Academy of Sciences (UCAS)}, China}{2015.09 -- 2019.08}
\textit{B.Eng.} in Computer Science and Technology\\
{\small Thesis: Vehicle Trajectory Prediction Based on Deep Learning}\\
{\small Supervisor: Prof. Dongbin Zhao}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{CENTAI}, Italy}{2025.03 -- 2025.06}
\role{Visiting scholar} {\small Host: Dr. Francesco Bonchi $\mid$ Collaborator: Dr. Atsushi Miyauchi}

\datedsubsection{\textbf{Korea Advanced Institute of Science and Technology (KAIST)}, South Korea}{2021.09 -- 2022.02}
\role{Research assistant}
{\small Supervisor: Prof. Kijung Shin}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faBook\ Publications}
\textbf{(C: Conference / J: Journal / P: Preprint / W: Workshop / *: Equal contribution)}
\begin{itemize}[parsep=0.5ex]
  \item [{[C21]}]
  Geon Lee*, \underline{Fanchen Bu*}, Soo Yong Lee*, Sunwoo Kim, and Kijung Shin.
  ``Toward a Science of AI Agent Societies.''
  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD) 2026. (Blue Sky Ideas Track).}

  \item [{[P1]}]
  Jaewan Chun*, \underline{Fanchen Bu*}, Yeongho Kim, Atsushi Miyauchi, Francesco Bonchi, and Kijung Shin.
  ``A Survey on Centrality and Importance Measures in Hypergraphs: Categorization and Empirical Insights.''
  \textit{arXiv 2512.00107.}

  \item [{[C20]}]
  \underline{Fanchen Bu}, Ruochen Yang, Paul Bogdan, and Kijung Shin.
  ``Edge Probability Graph Models Beyond Edge Independency: Concepts, Analyses, and Algorithms.''
  \textit{IEEE International Conference on Data Mining (ICDM) 2025.}

  \item [{[C19]}]
  \underline{Fanchen Bu}, Geon Lee, Minyoung Choe, and Kijung Shin.
  ``Identifying Group Anchors in Real-World Group Interactions Under Label Scarcity.''
  \textit{IEEE International Conference on Data Mining (ICDM) 2025. (Short paper)}

  \item [{[C18]}]
  Hyunjin Choo, \underline{Fanchen Bu}, Hyunjin Hwang, Young-Gyu Yoon, and Kijung Shin.
  ``HyperSearch: Prediction of New Hyperedges through Unconstrained yet Efficient Search.''
  \textit{IEEE International Conference on Data Mining (ICDM) 2025.}
  
  \item [{[C17]}]
  \underline{Fanchen Bu} and Kijung Shin.
  ``PyTorch-based Geometric Learning with Non-CUDA Processing Units: Experiences from Intel Gaudi-v2 HPUs.''
  \textit{Korea Computer Congress (KCC) 2025.}
  
  \item [{[C16]}]
  Federico Berto*, Chuanbo Hua*, Junyoung Park*, Laurin Luttmann*, Yining Ma, \underline{Fanchen Bu}, Jiarui Wang, Haoran Ye, and 22 Other Authors.
  ``RL4CO: an Extensive Reinforcement Learning for Combinatorial Optimization Benchmark.''
  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD) 2025. (Oral)}

  \item [{[C15]}]
  Langzhang Liang, \underline{Fanchen Bu}, Zixing Song, Zenglin Xu, Shirui Pan, and Kijung Shin.
  ``Mitigating Over-Squashing in Graph Neural Networks by Spectrum-Preserving Sparsification.''
  \textit{International Conference on Machine Learning (ICML) 2025.}
  
  \item [{[C14]}]
  Hyeonsoo Jo, Jongha Lee, \underline{Fanchen Bu}, and Kijung Shin.
  ``TiGer: Self-Supervised Purification for Time-evolving Graphs.''
  \textit{Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD) 2025.}

  \item [{[C13]}] 
  Junghun Lee, Hyunju Kim, \underline{Fanchen Bu}, Jihoon Ko, Kijung Shin.
  ``DiffIM: Differentiable Influence Minimization with Surrogate Modeling and Continuous Relaxation.''
  \textit{AAAI Conference on Artificial Intelligence (AAAI) 2025.}
  
  \item [{[C12]}] 
  Hyeonsoo Jo*, Hyunjin Hwang*, \underline{Fanchen Bu}, Soo Yong Lee, Chanyoung Park, and Kijung Shin.
  ``On Measuring Unnoticeability of Graph Adversarial Attacks: Observations, New Measure, and Applications.''
  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD) 2025.}    

  \item [{[J5]}] 
  Geon Lee, Kyungho Kim, \underline{Fanchen Bu}, Langzhang Liang, and Kijung Shin
  ``Revisiting LightGCN: Unexpected Inflexibility, Inconsistency, and A Remedy Towards Improved Recommendation.''
  \textit{ACM Transactions on Recommender Systems (TORS) 2025.}
  
  \item [{[J4]}] 
  Geon Lee*, \underline{Fanchen Bu*}, Tina Eliassi-Rad, and Kijung Shin.
  ``A Survey on Hypergraph Mining: Patterns, Tools, and Generators.''
  \textit{ACM Computing Surveys (CSUR) 2025.}
  
  \item [{[J3]}] 
  Hyunju Kim*, Heechan Moon*, \underline{Fanchen Bu}, Jihoon Ko, and Kijung Shin.
  ``Estimating Simplet Counts via Sampling.''
  \textit{The VLDB Journal 2025.}

  \item [{[W1]}]
  \underline{Fanchen Bu} and Kijung Shin.
  ``On Training-Test (Mis)alignment in Unsupervised Combinatorial Optimization: Observation, Empirical Exploration, and Analysis.''
  \textit{Workshop on Test-Time Adaptation @ International Conference on Machine Learning (ICML) 2025.}

  \item [{[C11]}]
  Sunwoo Kim, Soo Yong Lee, \underline{Fanchen Bu}, Shinhwan Kang, Kyungho Kim, Jaemin Yoo, and Kijung Shin.
  ``Rethinking Reconstruction-based Graph-Level Anomaly Detection: Limitations and a Simple Remedy.''
  \textit{Conference on Neural Information Processing Systems (NeurIPS) 2024.}
  
  \item [{[C10]}]
  \underline{Fanchen Bu}, Hyeonsoo Jo, Soo Yong Lee, Sungsoo Ahn, and Kijung Shin.
  ``Tackling Prevalent Conditions in Unsupervised Combinatorial Optimization: Cardinality, Minimum, Covering, and More.''
  \textit{International Conference on Machine Learning (ICML) 2024.}
  
  \item [{[C9]}]
  Soo Yong Lee, Sunwoo Kim, \underline{Fanchen Bu}, Jaemin Yoo, Jiliang Tang, and Kijung Shin.
  ``Feature Distribution on Graph Topology Mediates the Effect of Graph Convolution: Homophily Perspective.''
  \textit{International Conference on Machine Learning (ICML) 2024.}

  \item [{[C8]}]
  Sunwoo Kim, Shinhwan Kang, \underline{Fanchen Bu}, Soo Yong Lee, Jaemin Yoo, and Kijung Shin.
  ``HypeBoy: Generative Self-Supervised Representation Learning on Hypergraphs.''
  \textit{International Conference on Learning Representations (ICLR) 2024.}
  
  \item [{[C7]}]
  Hyeonsoo Jo, \underline{Fanchen Bu}, and Kijung Shin.
  ``Robust Graph Clustering via Meta Weighting for Noisy Graphs.''
  \textit{ACM International Conference on Information and Knowledge Management (CIKM) 2023.}
  
  \item [{[C6]}]
  \underline{Fanchen Bu} and Kijung Shin.
  ``On Improving the Cohesiveness of Graphs by Merging Nodes: Formulation, Analysis, and Algorithms.''
  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD) 2023.}
  
  \item [{[C5]}]
  Sunwoo Kim, \underline{Fanchen Bu}, Minyoung Choe, Jaemin Yoo, and Kijung Shin.
  ``How Transitive Are Real-World Group Interactions? - Measurement and Reproduction.''
  \textit{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD) 2023.}

  \item [{[C4]}]
  Soo Yong Lee, \underline{Fanchen Bu}, Jaemin Yoo, and Kijung Shin.
  ``Towards Deep Attention in Graph Neural Networks: Problems and Remedies.''
  \textit{International Conference on Machine Learning (ICML) 2023.}
  
  \item [{[C3]}]
  Hyunju Kim, Jihoon Ko, \underline{Fanchen Bu}, and Kijung Shin.
  ``Characterization of Simplicial Complexes by Counting Simplets Beyond Four Nodes.''
  \textit{ACM Web Conference (WWW) 2023.}
  
  \item [{[J2]}]
  \underline{Fanchen Bu}, Shinhwan Kang, and Kijung Shin.
  ``Interplay between Topology and Edge Weights in Real-World Graphs: Concepts, Patterns, and an Algorithm.''
  \textit{Data Mining and Knowledge Discovery (DAMI) 2023.}
  
  \item [{[J1]}]
  \underline{Fanchen Bu}, Geon Lee, and Kijung Shin.
  ``Hypercore Decomposition for Non-Fragile Hyperedges: Concepts, Algorithms, Observations, and Applications.''
  \textit{Data Mining and Knowledge Discovery (DAMI) 2023.}    

  \item [{[C2]}]
  \underline{Fanchen Bu} and Dong Eui Chang.
  ``Feedback Gradient Descent: Efficient and Stable Optimization with Orthogonality for DNNs.''
  \textit{AAAI Conference on Artificial Intelligence (AAAI) 2022.}

  \item [{[C1]}]
  \underline{Fanchen Bu} and Dong Eui Chang.
  ``Double Prioritized State Recycled Experience Replay.''
  \textit{IEEE International Conference on Consumer Electronics - Asia (ICCE-Asia) 2020.} 
\end{itemize}

\section{\faPencil\ Academic Services}
\textbf{(C: Conference / J: Journal)}
\begin{itemize}[parsep=0.5ex]
\item [{[C11]}] International Conference on Learning Representations (ICLR):
\begin{itemize}
    \item Reviewer: 2026
\end{itemize}
\item [{[C10]}] AAAI Conference on Artificial Intelligence (AAAI): 
\begin{itemize}
    \item Reviewer: 2026
\end{itemize}
\item [{[C9]}] ACM International Conference on Information and Knowledge Management (CIKM): 
\begin{itemize}
    \item Reviewer: 2025 -- 2026
    \item Session Chair: 2025
\end{itemize}
\item [{[C8]}] Conference on Neural Information Processing Systems (NeurIPS): 
\begin{itemize}
    \item Reviewer: 2025 -- 2026
\end{itemize}
\item [{[C7]}] The International Conference on Machine Learning (ICML): 
\begin{itemize}
    \item Reviewer: 2025 -- 2026
\end{itemize}
\item [{[C6]}] Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD): 
\begin{itemize}
    \item Workshop organizer: 2025
\end{itemize}
\item [{[C5]}] ACM Web Conference (WWW): 
\begin{itemize}
    \item Reviewer: 2025 -- 2026
\end{itemize}
\item [{[C4]}] Learning on Graphs Conference (LoG): 
\begin{itemize}
    \item Reviewer: 2024
\end{itemize}
\item [{[C3]}] European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML PKDD):
\begin{itemize}
    \item Reviewer: 2024
\end{itemize}
\item [{[C2]}] Asian Conference on Machine Learning (ACML): 
\begin{itemize}
    \item Reviewer: 2024 -- 2025
\end{itemize}
\item [{[C1]}] ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD):
\begin{itemize}
    \item Reviewer: 2024 -- 2026
\end{itemize}
\item [{[J10]}] PLoS One:
\begin{itemize}
    \item Reviewer: 2026
\end{itemize}
\item [{[J9]}] Neural Processing Letters:
\begin{itemize}
    \item Reviewer: 2025
\end{itemize}
\item [{[J8]}] The VLDB Journal:
\begin{itemize}
    \item Reviewer: 2025
\end{itemize}
\item [{[J7]}] Computational and Mathematical Organization Theory:
\begin{itemize}
    \item Reviewer: 2025
\end{itemize}
\item [{[J6]}] Scientific Reports:
\begin{itemize}
    \item Reviewer: 2025
\end{itemize}
\item [{[J5]}] IEEE Transactions on Pattern Analysis and Machine Intelligence (TPAMI):
\begin{itemize}
    \item Reviewer: 2025
\end{itemize}
\item [{[J4]}] International Journal of Machine Learning and Cybernetics (IJMLC):
\begin{itemize}
    \item Reviewer: 2024
\end{itemize}
\item [{[J3]}] IEEE Transactions on Network Science and Engineering (TNSE):
\begin{itemize}
    \item Reviewer: 2024
\end{itemize}
 \item [{[J2]}] The Journal of Supercomputing:
 \begin{itemize}
    \item Reviewer: 2024
\end{itemize}
 \item [{[J1]}] Big Data Research:
 \begin{itemize}
    \item Reviewer: 2024
\end{itemize}
 \end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{One of the top reviewers (top 200) in ICLR'26}{2026}
\datedline{One of the Gold reviewers (top 25\%) in ICML'26}{2026}
\datedline{One of the outstanding reviewers (top 10\%) in KDD'25 (both August and February Cycles)}{2025}
\datedline{One of the top reviewers (top 32) in LoG'24}{2024}

\section{\faLanguage\ Languages}
\begin{itemize}[parsep=0.5ex]  
  \item Chinese: Native
  \begin{itemize}
      \item Native: Mandarin and Wu Chinese
      \item Intermediate: Cantonese
      \item Elementary: Hokkien
  \end{itemize}
  \item English: Advanced
  \begin{itemize}
      \item IELTS 7.5
      \item GRE 333
  \end{itemize}
  \item Korean: Intermediate
  \item Italian: Elementary
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
